# Probability {#probability}

In this chapter we will discuss the probability as a framework for working with uncertainty. We'll start by defining probability then move to the *axioms* of probability. We'll talk about different *types* of probability that cover scenarios for complex events when some characteristics of the outcome are known. We'll then move on to *rules* of probability that permit us to manipulate probabilities.

Probability is used to talk about the plausibility of events. Sometimes the co-occurrence of events gives us additional information (if someone one is wealthy, they may also wear designer labels). However, sometimes the co-occurrence gives us no additional information. We will talk about *independence* and *conditional independence*.

Probability is tricky and associated with a number of *fallacies*, which we will discuss. This forms a subset of fallacies associated with data analysis in general which we will cover in a later chapter. Finally, we'll go over some applications of probability and the role of *simulation* in solving problems involving probability.


```{r child='source/probability/systems.Rmd', echo=FALSE}
```

```{r child='source/probability/definition.Rmd', echo=FALSE}
```

```{r child='source/probability/axioms.Rmd', echo=FALSE}
```

```{r child='source/probability/types.Rmd', echo=FALSE}
```

```{r child='source/probability/rules.Rmd', echo=FALSE}
```

```{r child='source/probability/independence.Rmd', echo=FALSE}
```

```{r child='source/probability/fallacies.Rmd', echo=FALSE}
```

```{r child='source/probability/applications.Rmd', echo=FALSE}
```

```{r child='source/probability/cities.Rmd', echo=FALSE}
```

```{r child='source/probability/conclusion.Rmd', echo=FALSE}
```

